TODO \thanks{ The original version of this paper is entitled ``Interactive Checks for Coordination Avoidance'' and was published in PVLDB Vol.\ 12. }

### 2020-05-16 doc/sigmod_paper/sections/abstract.tex
Copied VLDB to SIGMOD.
I copied over the VLDB paper but ported it to the SIGMOD style files.
Now, we just have to trim!
Fixed copyright.
The publisher gave us some specific instructions on what the copyright
should say. Hopefully, I've done this right.

In this paper, we establish conditions under which a commonly used sufficient
condition for \invariantconfluence{} is both necessary and sufficient, and we use
this condition to design (a) a general-purpose interactive
\invariantconfluence{} decision procedure and (b) a novel sufficient condition
that can be checked automatically. We then take a step beyond
\invariantconfluence{} and introduce a generalization of \invariantconfluence{},
called segmented \invariantconfluence{}, that allows us to replicate
non-\invariantconfluent{} objects with a small amount of coordination.

We implemented these formalisms in a prototype called Lucy and found that our
decision procedures efficiently handle common real-world workloads including
foreign keys, rollups, escrow transactions, and more.  We also found that
segmented \invariantconfluent{} replication can deliver up to an order of
magnitude more throughput than linearizable replication for low contention
workloads and comparable throughput for medium to high contention workloads.

\keywords{consistency, transactions, program analysis, invariants}
\end{abstract}

>>>>

In this paper, we establish conditions under which a commonly used sufficient
condition for \invariantconfluence{} is both necessary and sufficient, and we
use this condition to design a general-purpose interactive
\invariantconfluence{} decision procedure. We then take a step beyond
\invariantconfluence{} and introduce a generalization of
\invariantconfluence{}, called segmented \invariantconfluence{}, that allows us
to replicate non-\invariantconfluent{} objects with a small amount of
coordination.
%
We implemented these formalisms in a prototype called Lucy and found that our
decision procedures efficiently handle common real-world workloads including
%
% foreign keys, rollups, escrow transactions, and more.
foreign keys, escrow transactions, and more.
%
We also found that segmented \invariantconfluent{} replication can deliver up
to an order of magnitude more throughput than linearizable replication.
% for low contention workloads and comparable throughput for medium to high
% contention workloads.
\end{abstract}
